\section{Conclusions and Future Work}
\label{sec:conclusion}

In this paper, we have conducted extensive studies of system and application behavior using various job placement and routing configurations on a dragonfly network. We took a simulation-based approach, utilizing the CODES simulation toolkit and related models for high-fidelity dragonfly simulation, driving the network with three production-representative scientific application traces. We found that, under the prevailing recommendation of random job placement and adaptive routing, 
%the network effectively distributes the workload traffic to achieve a balanced load and strong overall performance, 
network traffic can be well distributed to achieve a balanced load and strong overall performance, 
at the cost of impairing jobs with less intensive communication patterns. We denoted this as the ``bully" effect. On the other hand, contiguous process placement prevents such effects while exacerbating local congestion, though this can be mitigated through the addition of adaptive routing. 
Finally, we performed initial experimentation exploring a mock ``hybrid'' contiguous/random job placement policy and two other random placement policies. 
Our preliminary study demonstrates the need of specialized job placement strategy based on application communication characteristics. 
We believe the findings and methodology presented in this paper provide valuable insights for efficient workload management on dragonfly networks, hence being valuable to the broad HPC community.


%\TODO{more future work here?}
In the future, we plan to explore intelligent job placement and routing configurations for diversified workloads running on the dragonfly network. The dragonfly connected system could have dedicated job placement and routing configuration based on the characteristics of its workload. We plan to collect workload traces from a production HPC system, and experiment with the simulated network of the system to explore the dedicated optimal job placement and routing configuration. We envision that effectiveness of such new placement and routing polices can be examined in future on a configurable dragonfly system. 

We also plan to study more details about application communication characteristics. The communication intensity discussed in this work is one the most prominent factors with regard to application communication behavior. Other important factors, such as communication frequency, operation dependency, the critical path in communication pattern, etc., should also be taken into consideration when choosing the proper placement and routing configuration. We believe that the more we know about the communication characteristics of applications, the better we can provide them with allocation that guaranteeing their optimal communication performance.









